### 2020-01-13 Study.Rmd
First Documentation Added

---
title: "Complete OverView"
author: "Andrew Maloney"
date: "1/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r eval=FALSE}
# Loading Packages
library(dplyr)
library(bulletxtrctr)
library(x3ptools)
library(ggplot2)
library(readr)
library(purrr)
library(stringr)
library(tidyr)
```

# This will be a complete description of
- Scripts for Feature Extraction
- Package Information
- Session_Info

Data 
- Which Scans are excluded
- meta file for data source(s)

- Examination of CMS feature extraction from bulletxtrctr

We are using three separate data sources: Hamby_173 & Hamby_252, Phoenix, and Houston Set Rescan

## Scripts for Feature Extraction

For Feature Extraction we are currently using the bulletxtrctr package.  Given a scanned bullet land in an x3p file format, we can extract many important features from two aligned signatures.

A typical pipeline would be something like this:

1. Read in bullets from a data source
2. Make sure the orientation is the same/correct for all scanned bullets
3. Obtain the Crosssections
4. Obtain CrossCuts
5. Correctly identify the groove cutoffs for each scanned bullet
6. Obtain the Signatures of each scanned bullet
7. Align signatures between each bullet and perform feature extraction

#### 1. Read in bullets from a datasource
The reading of a scanned bullet's x3p file can be done multiple ways, it really comes down to how you want your starting data to be labeled.

Hamby(173 & 252)

For Hamby 173 & 252 we are using the stringr, dplyr, and x3ptools packages to read and format the data.

* The files are in the form .x3p
* The list should recurse into directories(recursive = TRUE)
* The directory path is prepended(full.names = TRUE)
* The path is stored and read as x3p(read_x3p)

#### 2. Orientation
Using the x3ptools package we are able to adjust the orientation of the scanned bullets to meet our needs

* The x3p information is converted to microns from meters(x3p_m_to_mum(.))
* We define the y-axis in reference to the bottom right corner(y_flip_x3p())
* An x3p object may need to be rotated inorder to conform to ISO standards, like in the case of hamby 252.

[default parameters] -> rotate_x3p(x3p_object, angle = 90, 180, 270, -90, -180, -270)

```{r eval=FALSE}

df <- tibble(path = list.files(path = file.path(data_dir, "Hamby_173"), 
                               pattern = ".x3p", recursive = T, 
                               full.names = T)) %>% 
  mutate(Barrel = str_extract(path, "(Unknown|Barrel)\\d{0,2}") %>% 
           str_remove("Barrel"), 
         Bullet = str_extract(path, "Bullet[12A-Z]") %>% 
           str_remove("Bullet"),
         Land = str_extract(path, "land\\d{1}") %>% 
           str_remove("land")) %>% 
  mutate(Set = "Hamby173") %>%
  mutate(x3p = map(path, read_x3p)) %>%
  mutate(x3p = map(x3p, ~x3p_m_to_mum(.) %>% y_flip_x3p()))

df2 <- tibble(path = list.files(path = file.path(data_dir, "Hamby_252"), 
                                pattern = ".x3p", recursive = T, 
                                full.names = T)) %>% 
  mutate(Barrel = str_extract(path, "(Unknown|Barrel)\\d{0,2}") %>% 
           str_remove("Barrel"), 
         Bullet = str_extract(path, "Bullet[12A-Z]") %>% 
           str_remove("Bullet"), 
         Land = str_extract(path, "Bullet [12A-Z]-[123456]") %>% 
           str_remove("Bullet [12A-Z]-")) %>% 
  mutate(Set = "Hamby252") %>%
  mutate(x3p = map(path,read_x3p))  %>%
  # Adjust orientation
  mutate(x3p = map(x3p, ~x3p_m_to_mum(.) %>% rotate_x3p(angle = -90) %>% y_flip_x3p()))

```

#### 3. Obtain Cross Sections
We can use the bulletxtrctr and purrr packages to obtain cross sections

x3p_crosscut_optimize allows us to identify a cross section that is close to the heal of the bullet and does not suffer from defects(break-off, pitting, ... , etc)

* distance: distance between crossections for comparison
* ylimits: manually assign where to check for reliable cross-sections
* minccf: min value of cross-correlation for a region
* span: span of loess smooth 
* percent_missing: how much of the section is damaged or missing to be allowed for reliable cross-section

[default parameters] -> x3p_crosscut_optimize(x3p_object, distance = 25, ylimits = c(50, NA), minccf = 0.9, span = 0.03, percent_missing = 50)

We applied a smaller value for percent_missing which is a more strict constraint.  The idea behind this was we would get a region more to our liking.

```{r eval=FALSE}
# Cross Sections

hamby <- hamby %>%
  mutate(CrossSection = 
           map_dbl(x3p, x3p_crosscut_optimize, minccf = 0.9, span = 0.3, percent_missing = 25))

```

#### 4. Obtain Cross Cuts
Using the x3p_crosscut function from bulletxtrctr we are able to read a crosscut given an x3p object and a cross section

* y: level of crosscut 
* range: range to be extracted

[default parameters] -> x3p_crosscut(x3p_object, y = NULL, range = 1e-05)

We are using the standard defaults for Hamby 173 & 252

```{r eval=FALSE}

hamby <- hamby %>% 
  mutate(CrossCut = map2(.x = x3p, .y = CrossSection, .f = x3p_crosscut))

```

#### 5. Obtain Grooves and correctly identify groove cut offs
Using the cc_locate_grooves function from bulletxtrctr we can find the grooves for a Barrel-Bullet-Land scan.

* ccdata: our dataframe of the crosscuts
* method: method for identifying grooves (rollapply, quadratic, middle, logisticlegacy, lassobasic, lassofull, bcp)
* smoothfactor: smoothing window
* adjust: adjust grooves
* groove_cutoff: cutoff for grooves
* mean_left: average left groove
* mean_right: average of right groove
* mean_window: window around left & right grooves
* return_plot: return a plot of the grooves that are extracted

[default parameters] -> cc_locate_grooves(ccdata, method = "rollapply", smoothfactor = 15, adjust = 10, groove_cutoff = 400, mean_left = NULL, mean_right = NULL, mean_window = 100, return_plot = FALSE)

Currently this function is still not performing to a standard we are comfortable with so we are using a interactive shiny app to correct the mistakes of this function.

```{r eval=FALSE}

#Grooves
hamby173 <- hamby173 %>% 
    mutate(Grooves = CrossCut %>% 
             map(.f = cc_locate_grooves, 
                        method = "rollapply", smoothfactor = 15, return_plot = T))  # use plot so that the shiny app works...

hamby252 <- hamby252 %>% 
    mutate(Grooves = CrossCut %>% 
             map(.f = cc_locate_grooves, 
                        method = "rollapply", smoothfactor = 15, return_plot = T))  # use plot so that the shiny app works...

```

#### 6. Obtain the signatures
After we have correctly identified the groove cutoffs we are able to extract the signature information.
Using the cc_get_signature function from bulletxtrctr

* ccdata: Crosscut data
* grooves: Grooves data
* span1: 
* span2:

[default parameters] -> cc_get_signature(ccdata, grooves, span1 = 0.75, span2 = 0.03)

We are using the current defaults

```{r eval=FALSE}

hamby173 <- hamby173 %>% 
  mutate(Signatures = map2(.x = CrossCut, .y = Grooves, .f = cc_get_signature, span = 0.75, span2 = .03))

hamby252 <- hamby252 %>% 
  mutate(Signatures = map2(.x = CrossCut, .y = Grooves, .f = cc_get_signature, span = 0.75, span2 = .03))

```

#### 7. Feature Extraction
We are now able to perform feature extraction given two aligned signatures.

* we can align two signatures(sig1, sig2) using sig_align function from bulletxtrctr, sig_align only uses each group of 2 signatures.
* Next we find the CMS between two signatures using sig_cms_max function from bulletxtrctr.

[default parameters] -> sig_cms_max(alignment_data, span = 35)

* Once we have obtained are aligned and striae data we are able to extract many different features.
* We extract the rest of these features using the extract_features_all function from bulletxtrctr
* there is also a legacy version of the extract_features_all function

[default parameters] -> extract_features_all(aligned, striae, resolution, tmpfile = NULL)

```{r eval=FALSE}
plan(multicore)

get_sig <- function(data) {
  map(data$Signatures, "sig")
}
comparisons_173 <- comparisons_173 %>%
  mutate(sig1 = map(Bullet1_data, get_sig), sig2 = future_map(Bullet2_data, get_sig))

comparisons_173 <- comparisons_173 %>%
  mutate(Aligned = map2(sig1, sig2, ~sig_align(unlist(.x), unlist(.y)))) # Getting Aligned signatures

# Get striae
comparisons_173 <- comparisons_173 %>%
  mutate(Striae = map(Aligned, sig_cms_max)) # Obtaining Striae

saveRDS(select(comparisons_173, -Bullet1_data, -Bullet2_data), file = "Hamby_173Comparisons.rda")

comparisons_173 <- comparisons_173 %>% 
  select(-Bullet1_data, -Bullet2_data)

get_sig <- function(data) {
  map(data$Signatures, "sig")
}
comparisons_252 <- comparisons_252 %>%
  mutate(sig1 = map(Bullet1_data, get_sig), sig2 = future_map(Bullet2_data, get_sig))

comparisons_252 <- comparisons_252 %>%
  mutate(Aligned = map2(sig1, sig2, ~sig_align(unlist(.x), unlist(.y)))) # Getting Aligned signatures

# Get striae
comparisons_252 <- comparisons_252 %>%
  mutate(Striae = map(Aligned, sig_cms_max)) # Obtaining Striae

saveRDS(select(comparisons_252, -Bullet1_data, -Bullet2_data), file = "Hamby_252Comparisons.rda")

comparisons_252 <- comparisons_252 %>% 
  select(-Bullet1_data, -Bullet2_data)

#--------------------------------------------------------------------------------------------------#

comparisons_173 <- comparisons_173 %>% 
  mutate(features = map2(Aligned, Striae, extract_features_all, resolution = 1.5625)) #ObtainingFeatures

comparisons_173 <- comparisons_173 %>% 
  mutate(Legacy_Features = map(Striae, extract_features_all_legacy, resolution = 1.5625)) # Obtaining feature leacy

comparisons_legacy_173 <- comparisons_173 %>% 
  select(-features) %>%
  tidyr::unnest(Legacy_Features) # Extracting feature legacy

comparisons_173 <- comparisons_173 %>%
  select(-Legacy_Features) %>%
  tidyr::unnest(features)

comparisons_252 <- comparisons_252 %>% 
  mutate(features = map2(Aligned, Striae, extract_features_all, resolution = 1.5625)) #ObtainingFeatures

comparisons_252 <- comparisons_252 %>% 
  mutate(Legacy_Features = map(Striae, extract_features_all_legacy, resolution = 1.5625)) # Obtaining feature leacy

comparisons_legacy_252 <- comparisons_252 %>% 
  select(-features) %>%
  tidyr::unnest(Legacy_Features) # Extracting feature legacy

comparisons_252 <- comparisons_252 %>%
  select(-Legacy_Features) %>%
  tidyr::unnest(features)

head(comparisons_252, 50)
```

$------------------------------------------------------------------------------------------------------------------------------$

Houston Set Rescan

We apply the same techniques to Houston that we showed previously with some minor adjustments.

#### 1. Read in bullets from a datasource
Houston is comprised of three groups of bullet scans which are Group1, Group2, and Group3.
The files come originally in a .dat file type.

Using stringr, dplyr, and x3ptools we can read in each group of bullet scans.

* The list should recurse into directories(recursive = TRUE)
* The directory path is prepended(full.names = TRUE)
* The path is stored and read by converted from to .dat to .x3p

[default parameters] -> x3p_read_dat(dat_object, delim = " ", col_names = FALSE)

Each group was read in separately

```{r eval=FALSE}

Group1 <- tibble(path = list.files(path = "/media/Sunny/CSAFE/Houston Set Rescan/Group 1",
                 pattern = ".dat", recursive = T,
                 full.names = T)) %>%
  mutate(Barrel = str_extract(path, "(Unknowns|K[A-Z])\\d{0,2}"),
         Bullet = str_extract(path, "(Bullet [123A-Z]|U[0-9][0-9])") %>% 
                              str_remove("Bullet"),
         Land = str_extract(path, "Land [0-9]") %>%
                              str_remove("Land")) %>%
  mutate(Set = "Group_1") %>% 
  mutate(dat = future_map(path, x3p_read_dat))

```

#### 2. Orientation

Using the x3ptools package we can make the y-axis in reference to the bottom right corner(y_flip_x3p())
Again this is to meet the current ISO standards.

You can see a function called future_map from the furrr package, this is works the same at the function map from purrr but runs processes parallel.  This was more of a learning thing and should be replaced with map.

```{r eval=FALSE}

Group1 <- Group1 %>% mutate(
  dat = dat %>% future_map(.f = function(x) x %>% 
                             y_flip_x3p()))
```

#### 3. Obtain Cross Sections
We can use the bulletxtrctr and purrr packages to obtain cross sections.

[default parameters] -> x3p_crosscut_optimize(x3p_object, distance = 25, ylimits = c(50, NA), minccf = 0.9, span = 0.03, percent_missing = 50)

We would like to extract the crosssection as close to the heel of the bullet as possible but what we found were many types of damages or impurities near the lower regions of the Houston scans.

For Houston, each Barrel for each group had multiple different ylimits due to it being very hard to find stable regions.
Below is an example showing what we did for group 1.

```{r eval=FALSE}

Group1 <- Group1 %>%
  mutate(CrossSection = future_map_dbl(x3p, x3p_crosscut_optimize, ylimits = c(150 ,NA)))

Group1_Barrel_KA <- Group1_Barrel_KA %>%
  mutate(CrossSection = future_map_dbl(x3p, x3p_crosscut_optimize, ylimits = c(350, NA)))

Group1_Barrel_KB <- Group1_Barrel_KB %>%
  mutate(CrossSection = future_map_dbl(x3p, x3p_crosscut_optimize, ylimits = c(300, NA)))

Group1_Barrel_KC <- Group1_Barrel_KC %>%
  mutate(CrossSection = future_map_dbl(x3p, x3p_crosscut_optimize, ylimits = c(300, NA)))

Group1_Barrel_KD <- Group1_Barrel_KD %>%
  mutate(CrossSection = future_map_dbl(x3p, x3p_crosscut_optimize, ylimits = c(300, NA)))

Group1_Barrel_KE <- Group1_Barrel_KE %>%
  mutate(CrossSection = future_map_dbl(x3p, x3p_crosscut_optimize, ylimits = c(300, NA)))

Group1_Barrel_Unknons <- Group1_Barrel_Unknons %>%
  mutate(CrossSection = future_map_dbl(x3p, x3p_crosscut_optimize, ylimits = c(250, NA)))

Group1 <- bind_rows(Group1, Group1_Barrel_KA, Group1_Barrel_KB, Group1_Barrel_KC, Group1_Barrel_KD, Group1_Barrel_KE, Group1_Barrel_Unknons)

```

#### 4. Obtain Cross Cuts
[default parameters] -> x3p_crosscut(x3p_object, y = NULL, range = 1e-05)

Now that we identified stable regions we can obtain crosscuts for each group.

```{r eval=FALSE}

Group1 <- Group1 %>% 
  mutate(CrossCut = future_map2(.x = x3p, .y = CrossSection, .f = x3p_crosscut))

```

#### 5. Obtain Grooves and correctly identify groove cut offs

[default parameters] -> cc_locate_grooves(ccdata, method = "rollapply", smoothfactor = 15, adjust = 10, groove_cutoff = 400, mean_left = NULL, mean_right = NULL, mean_window = 100, return_plot = FALSE)

Currently this function is still not performing to a standard we are comfortable with so we are using a interactive shiny app to correct the mistakes of this function.

```{r eval=FALSE}

Group1 <- Group1 %>% 
    mutate(Grooves = CrossCut %>% 
             future_map(.f = cc_locate_grooves, 
                        method = "rollapply", smoothfactor = 15, return_plot = T))

```

#### 6. Obtain the signatures

Early we mentioned about manually setting the ylimit when obtaining a cross sections.  This was because we wanted to find a stable region to get the crosscuts for each scan but also because we needed our residuals to be within -10 to 10 along the y-axis.

[default parameters] -> cc_get_signature(ccdata, grooves, span1 = 0.75, span2 = 0.03)

```{r eval=FALSE}

Group1 <- Group1 %>% 
 mutate(Signatures = future_map2(.x = CrossCut, .y = Grooves, .f = cc_get_signature, span = 0.75, span2 = .03))

```

#### 7. Feature Extraction
We are now able to perform feature extraction given two aligned signatures.

[default parameters] -> extract_features_all(aligned, striae, resolution, tmpfile = NULL)

$-------------------------------------------------------------------------------------------------------------------------$

Phoenix

We apply the same techniques as we did for Hamby & Houston to Phoenix.  
Phoenix had some of the highest scan quality out of the three groups.

#### 1. Read in bullets from a datasource
* The files are in the form .x3p
* The list should recurse into directories(recursive = TRUE)
* The directory path is prepended(full.names = TRUE)
* The path is stored and read as x3p(read_x3p)

#### 2. Orientation
Phoenix y-axis was already corret so no rotation or y_flip was applied

```{r eval=FALSE}
Phoenix <- tibble(path = list.files(path = "/media/Sunny/CSAFE/Phoenix Set",
                                     pattern = ".x3p", recursive = T, full.names = T)) %>% 
   mutate(Barrel = str_extract(path, "(Unknown|Gun [0-9]-[A-Z][0-9])") %>%
            str_remove("Gun 1-"),
          Bullet = str_extract(path, "(B[0-9]|Unknown 1-[A-Z])") %>%
            str_remove("Unknown 1-"), 
          Land = str_extract(path, "/L[0-9]") %>% str_remove("/L")) %>%
   mutate(x3p = map(path, read_x3p))

```

#### 3. Obtain Cross Sections
We can use the bulletxtrctr to obtain cross sections.

[default parameters] -> x3p_crosscut_optimize(x3p_object, distance = 25, ylimits = c(50, NA), minccf = 0.9, span = 0.03, percent_missing = 50)

```{r eval=FALSE}

Phoenix <- Phoenix %>%
  mutate(CrossSection = future_map_dbl(x3p, x3p_crosscut_optimize, span = 0.03))

```

#### 4. Obtain Cross Cuts
[default parameters] -> x3p_crosscut(x3p_object, y = NULL, range = 1e-05)

Now that we identified stable regions we can obtain crosscuts for each group.

```{r eval=FALSE}

Phoenix <- Phoenix %>% 
  mutate(CrossCut = map2(.x = x3p, .y = CrossSection, .f = x3p_crosscut))

```

#### 5. Obtain Grooves and correctly identify groove cut offs

[default parameters] -> cc_locate_grooves(ccdata, method = "rollapply", smoothfactor = 15, adjust = 10, groove_cutoff = 400, mean_left = NULL, mean_right = NULL, mean_window = 100, return_plot = FALSE)

Currently this function is still not performing to a standard we are comfortable with so we are using a interactive shiny app to correct the mistakes of this function.

```{r eval=FALSE}

Phoenix <- Phoenix %>% 
    mutate(Grooves = CrossCut %>% 
             future_map(.f = cc_locate_grooves, 
                        method = "rollapply", smoothfactor = 15, return_plot = T))  # use plot so that the shiny app works...

```

#### 6. Obtain the signatures
[default parameters] -> cc_get_signature(ccdata, grooves, span1 = 0.75, span2 = 0.03)

```{r eval=FALSE}

Phoenix <- Phoenix %>% 
 mutate(Signatures = future_map2(.x = CrossCut, .y = Grooves, .f = cc_get_signature, span = 0.75, span2 = .03))

```

#### 7. Feature Extraction
We are now able to perform feature extraction given two aligned signatures.

* we can align two signatures(sig1, sig2) using sig_align function from bulletxtrctr, sig_align only uses each group of 2 signatures.
* Next we find the CMS between two signatures using sig_cms_max function from bulletxtrctr.

[default parameters] -> sig_cms_max(alignment_data, span = 35)

* Once we have obtained are aligned and striae data we are able to extract many different features.
* We extract the rest of these features using the extract_features_all function from bulletxtrctr
* there is also a legacy version of the extract_features_all function

[default parameters] -> extract_features_all(aligned, striae, resolution, tmpfile = NULL)

```{r eval=FALSE}

plan(multicore)

get_sig <- function(data) {
  map(data$Signatures, "sig")
}
Phoenix_Comparisons <- Phoenix_Comparisons %>%
  mutate(sig1 = future_map(Bullet1_data, get_sig), sig2 = future_map(Bullet2_data, get_sig))

Phoenix_Comparisons <- Phoenix_Comparisons %>%
  mutate(Aligned = future_map2(sig1, sig2, ~sig_align(unlist(.x), unlist(.y)))) # Getting Aligned signatures
# Get striae

Phoenix_Comparisons <- Phoenix_Comparisons %>%
  mutate(Striae = future_map(Aligned, sig_cms_max)) # Obtaining Striae

saveRDS(select(Phoenix_Comparisons, -Bullet1_data, -Bullet2_data), file = "Phoenix_Comp.rda")

Phoenix_Comparisons <- Phoenix_Comparisons %>% 
  select(-Bullet1_data, -Bullet2_data)

Phoenix_Comparisons <- Phoenix_Comparisons %>% 
  mutate(features = future_map2(.x = Aligned, .y = Striae, .f = extract_features_all, resolution = 1.5625))#ObtainingFeatures

```

## Excluded Scans

#### Hamby
There were no missing scans.

4 scans were later deemed to be unsuitable and were not used proceeding forward.

- Barrel 6 Bullet 2-1

- Barrel 9 Bullet 2-4

- Barrel Unknown Bullet B-2

- Barrel Unknown Bullet Q-4

Scans that should also be removed based on the case validation paper and scan.

- Barrel 1 Bullet 1-6

- Barrel 2 Bullet 2-5

- Barrel 3 Bullet 1-5

- Barrel 8 Bullet 1-6

- Barrel 8 Bullet 2-2

- Barrel 8 Bullet 2-6

- Barrel Unknown Bullet E-6

- Barrel Unknown Bullet I-6

#### Houston
There were no missing scans and all scans were used in the study.

#### Phoenix
There is some missing data in Phoenix.

We found that C8-B1-3 and U1-B3-5 are both missing.

All other scans were used in the study.

### 2020-01-13 Study.Rmd
First Documentation

@@
 
-x3p_crosscut_optimize allows us to identify a cross section that is close to the heal of the bullet and does not suffer from defects(break-off, pitting, ... , etc)
+x3p_crosscut_optimize allows us to identify a cross section that is close to the heel of the bullet and does not suffer from defects(break-off, pitting, ... , etc)
 

### 2020-04-28 Paper.Rmd
First Push
- All the Code for CMS and Model Comparisons have been run and stored
- Paper is currently work in Progress

---
title: "Stat_490"
author: "Andrew Maloney"
date: "4/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Consecutive Matching Striae

### Produced in R Markdown

- When a bullet is fired from a gun, there are distinct markings left on the bullet. These markings are generally caused by the spiral engravings inside of the barrel, the igniting of the powder propellant, or foreign matter inside the barrel. These distinctive markings allow for firearm examination to be conducted. Currently, the comparison of two bullets is a subjective process involving simultaneous visual examination of two bullets by a trained practitioner. Using 3D microscopy, the bullets can be numerically characterized and the matching process can be automated. When the bullet has been numerically characterized we are left with a set of quantitative 'features', each with there own column in a data set.  One of these features is known as CMS(Consecutive Matching Striae) and we will examine the underlying structure of how the CMS is calculated, how changing parameters used to calculate CMS affect the final calculation result for CMS.  We expand the scope of the matching algorithm by fitting a generalized random forest model using a wide range of different CMS calculation. With this expanded model, we expect that the algorithm’s results using different CMS calculations will lead to new insights on how 'important' CMS is as a feature and how different CMS impact the Accuracy of two bullets being a match or not a match.  We perform all of our calculations using the R and mulitple R Programming Language. Before we begin to examine the feature known as consecutive matching striae, we will need to perform a number of steps with the bullet scans(edit)

- For this paper we use the Phoenix data set which consist of 198 scanned bullets. The scanned bullets are in a .x3p file format of the surface scan between adjacent groove impressions on the bullet and can be read into R using the R package x3ptools. For this study we will exam two datasets.  One Phoenix dataset will have its x3p files containing the scanned bullets down sampled using the x3p_sample() function(See Figure 1).  When down sampling is performed the number of pixels in each x3p file are reduced down by a half vertically and horizontally.  The other Phoenix dataset will have no down sampling performed to the x3p files containg the scanned bullets(See Figure 2). We examine the scaled measurements of each bullet after being loaded into R. We use the function x3p_get_scale() from the x3ptools package to see what the scale is for each of the bullet scans in both datasets. The original measurement scale of the bullet depends on the microscope and scanner used to scan the bullet before being converted into an .x3p file format.  The Phoenix dataset with no sampling has a resolution of 0.654 and the sampled Phoenix dataset has a resolution of 1.29.  This makes sense because reducing the pixels by a half will result in a larger micron measurement.  *Note: as a final check we make sure that the base of the bullet are at the bottom of the scan.  The bottom of the bullet scan is known as the 'heel' of the bullet.*

(Figure 1): Image of scanned Bullet with Reduced Pixels

(Figure 2): Regular image of scanned Bullet

- We are now able to analyze the surface scan, by taking a cross section of the surface scan measurements.  This can be performed using the x3p_crosscut_optimize() function and then next the x3p_crosscut() function. Both of which are in the bulletxtrctr R package.  *Note: We will refer to the surface scan as a land impression from now on.* When plotting the crosscuts we are left with a side profile of the land impressions(See Figure 3). Notice the shape of the side profile, it resembles a perfect semi circle. If we think about the shape of a bullet and look at surface of the bullet outside its casing, we can take a pencil and sketch a 180 degree line along the bullet.  Which will give us the same semi circular shape.  Also notice the two hills on the left and right side of the cross sections.  These hills are known as shoulders and at the valleys of these shoulders is where the land impression starts and ends.  The shoulders contain no useful information to date and are removed.

(Figure 3): Side Profile of a bullets land impression

- We begin the process of removing the shoulders. First we identify the shoulder locations of each land impression(See Figure 4).  Second we smooth the land impression(See figure 5).  We then remove the shoulders of the land impression by specifying the left and right shoulder cutoffs.  Currently this process is trying to be automated using the cc_locate_grooves() function in the bulletxtrctr package but for this study we manually removed the shoulders of the smoothed land impression using a shiny app(See Figure 6).

[[[- Briefly compare the the down-sampled data and the non down-sampled data]]]

(Figure 4): Shoulder locations x2

(Figure 5): Smoothed Impression x2

(Figure 6): Shiny displaying the new groove cutoffs.

- After we have identified the groove cutoffs we look for the lowest stable region for each land impression and extract the signatures(See Figure 7).  The signatures can be obtained using the cc_get_signature() function in the bulletxtrctr package.

(Figure 7): Signature Plot

- In the beginning of this paper we talked about bullets being numerically characterized, which we said were features.  One of these features is CMS, also known as consecutive matching striae.  We are now able extract the CMS and all the other features associated with bullets land impression.  We first smooth the signatures(See Figure 8), identifiy peaks and valleys of each signature(See Figure 9), and align every signature with eachother(See Figure 10). When the two signatures are aligned we are able to identify the matching peaks and valleys which coincide to the striation marks left on a bullet's surface after being fired(See figure 11). This is done by using the sig_aligned() function in the bulletxtrctr package. Notice the word "striation," that's right these are our consecutive matching striae. We can calculate the consecutive matching striae using the sig_cms_max() function in the bulletxtrctr package.

(Figure 8): Show Smoothed Vs Non Smoothed(span = default)

(Figure 9): Show identified peaks and valleys

(Figure 10): Show Aligned Signatures

(Figure 11): cite and show actually markings associated with cms)

- We explore the maximum number of CMS using different values for the span parameter in sig_cms_max().  We run 8 different spans and compare the Maximum number of CMS

... to be continued

## Code Appendix

```{r}

#Loading Packages
library(dplyr)
library(bulletxtrctr)
library(x3ptools)
library(randomForest)
library(ggplot2)
library(readr)
library(purrr)
library(stringr)
library(tidyr)

```

```{r eval=FALSE}

Phoenix <- tibble(path = list.files(path = "/media/Sunny/CSAFE/Phoenix Set",
                                     pattern = ".x3p", recursive = T, full.names = T)) %>% 
   mutate(Barrel = str_extract(path, "(Unknown|Gun [0-9]-[A-Z][0-9])") %>%
            str_remove("Gun 1-"),
          Bullet = str_extract(path, "(B[0-9]|Unknown 1-[A-Z])") %>%
            str_remove("Unknown 1-"), 
          Land = str_extract(path, "/L[0-9]") %>% str_remove("/L")) %>%
   mutate(x3p = map(path, read_x3p))

```

```{r eval=FALSE}

image(Phoenix$x3p[[7]])
ggsave("No_Sampling.png")

Phoenix <- Phoenix %>% mutate(x3p = map(x3p, sample_x3p, m = 2)) # Down Sampling

image(Phoenix$x3p[[7]])
ggsave("Sampling.png")

```

```{r eval = FALSE}

Phoenix <- Phoenix %>%
  mutate(CrossSection = map_dbl(x3p, x3p_crosscut_optimize))

```

```{r eval = FALSE}

Phoenix <- Phoenix %>% 
  mutate(CrossCut = map2(.x = x3p, .y = CrossSection, .f = x3p_crosscut))

crosscuts_phoenix <- select(Phoenix, -path, -x3p) %>% 
      tidyr::unnest(CrossCut)

```

```{r eval=FALSE}
library(shiny)
if (file.exists(saved_grooves_location_Phoenix)) {
  Phoenix$Grooves <- readRDS(saved_grooves_location_Phoenix)
}
if (interactive()) { # only run when you're manually running chunks... don't run when the whole document is compiled.
  shinyApp(
    ui = fluidPage(
      selectInput("k", "Investigate kth plot:",
                  selected = 1,
                  choices = (1:length(Phoenix$Grooves)) %>% set_names(Phoenix$id)
      ),
      textOutput("groovelocations"),
      actionButton("confirm", "Confirm"),
      actionButton("save", "Save"),
      plotOutput("groovePlot", click = "plot_click"),
      verbatimTextOutput("info")
    ),

    server = function(input, output, session) {
      output$groovePlot <- renderPlot({
        k <- as.numeric(input$k)
        p <- Phoenix$Grooves[[k]]$plot

        p
      })
      output$groovelocations <- renderText({
        paste(
          "Left Groove: ", Phoenix$Grooves[[as.numeric(input$k)]]$groove[1],
          " Right Groove: ", Phoenix$Grooves[[as.numeric(input$k)]]$groove[2]
        )
      })
      observeEvent(input$confirm, {
        cat(paste(Phoenix$id[as.numeric(input$k)], "\n"))
        updateSelectInput(session, "k", "Investigate kth plot:",
                          selected = as.numeric(input$k) + 1,
                          choices = (1:length(Phoenix$Grooves)) %>% set_names(Phoenix$id)
        )
      })
      observeEvent(input$save, {
        saveRDS(Phoenix$Grooves, file = saved_grooves_location_Phoenix)
        message("groove data saved\n")
      })

      observeEvent(input$plot_click, {
        k <- as.numeric(input$k)
        xloc <- input$plot_click$x

        gr <- Phoenix$Grooves[[k]]$groove
        if (abs(gr[1] - xloc) < abs(gr[2] - xloc)) {
          Phoenix$Grooves[[k]]$groove[1] <<- xloc
        } else {
          Phoenix$Grooves[[k]]$groove[2] <<- xloc
        }
        output$groovePlot <- renderPlot({
          k <- as.numeric(input$k)
          p <- Phoenix$Grooves[[k]]$plot +
            geom_vline(xintercept = Phoenix$Grooves[[k]]$groove[1], colour = "green") +
            geom_vline(xintercept = Phoenix$Grooves[[k]]$groove[2], colour = "green")

          p
        })
      })
      output$info <- renderText({
        paste0("x=", input$plot_click$x, "\ny=", input$plot_click$y)
      })
    },
    options = list(height = 500)
  )
  saveRDS(Phoenix$Grooves, file = saved_grooves_location_Phoenix)
} else {
  if (!file.exists(saved_grooves_location_Phoenix)) {
    message("run script in interactive mode to fix grooves")
  } else {
    Phoenix$Grooves <- readRDS(saved_grooves_location_Phoenix)
  }
}

```

```{r eval = FALSE}

Phoenix <- Phoenix %>% 
 mutate(Signatures = future_map2(.x = CrossCut, .y = Grooves, .f = cc_get_signature, span = 0.75, span2 = .03))

 Signatures_Phoenix <- Phoenix %>% 
  select(id, Barrel, Bullet, Land, Signatures) %>% 
   tidyr::unnest()

```

```{r eval = FALSE}

Phoenix_Comparisons <- crossing(Bullet1 = Phoenix$id, Bullet2 = Phoenix$id) %>%
  left_join(nest(Phoenix, -id) %>% magrittr::set_names(c("Bullet1", "Bullet1_data"))) %>%
  left_join(nest(Phoenix, -id) %>% magrittr::set_names(c("Bullet2", "Bullet2_data")))

```

```{r eval = FALSE}

get_sig <- function(data) {
  map(data$Signatures, "sig")
}
Phoenix_Comparisons <- Phoenix_Comparisons %>%
  mutate(sig1 = map(Bullet1_data, get_sig), sig2 = map(Bullet2_data, get_sig))

Phoenix_Comparisons <- Phoenix_Comparisons %>% 
  select(-Bullet1_data, -Bullet2_data)

Phoenix_Comparisons <- Phoenix_Comparisons %>%
  mutate(Aligned = map2(sig1, sig2, ~sig_align(unlist(.x), unlist(.y))))

```

```{r eval = FALSE}

Phoenix_Comparisons <- Phoenix_Comparisons %>%
 mutate(Striae = map(Aligned, sig_cms_max, span = 15))

Phoenix_Comparisons <- Phoenix_Comparisons %>% 
  mutate(features = map2(.x = Aligned, .y = Striae, .f = extract_features_all, resolution = resolution_p))

Phoenix_Comparisons <- Phoenix_Comparisons_15 %>%
  tidyr::unnest(features)

```

### 2020-05-05 Paper.Rmd
Paper Update
- Added Summary Statistics for cms using span:
15, 25, 35, 45, 55, 65, 75, and 85
- Added ROC plots for cms using span:
15, 25, 35, 45, 55, 65, 75, 85
- Added AUC outputs for different spans
- Added Images(Still need some more and maybe need to remove some)
- Images are currently inserted using code chunk with the image path being on my personal computer
- Models are currently running for comparisons

@@
 ---
-title: "Stat_490"
+title: "Stat_490_Paper"
 author: "Andrew Maloney"
-date: "4/28/2020"
+date: "5/5/2020"
 output: html_document
@@
 
+![Scan 1 Sampled](/Users/piza7/Pictures/Paper_1_samp.png)
+
+![Scan 11 Sampled](/Users/piza7/Pictures/Paper_11_samp.png)
+
+![Scan 111 Sampled](/Users/piza7/Pictures/Paper_111_samp.png)
+
 (Figure 2): Regular image of scanned Bullet
+
+![Scan 1](/Users/piza7/Pictures/Paper_1_nosamp.png)
+
+![Scan 11](/Users/piza7/Pictures/Paper_11_nosamp.png)
+
+![Scan 111](/Users/piza7/Pictures/Paper_111_nosamp.png)
 
@@
 
+![Before Cutoff](/Users/piza7/Pictures/Paper_Groove_before_Cut.png)
+
+![Cutoff](/Users/piza7/Pictures/Paper_Groove_Cut.png)
+
 - After we have identified the groove cutoffs we look for the lowest stable region for each land impression and extract the signatures(See Figure 7).
@@
 (Figure 7): Signature Plot
+
+```{r, echo=FALSE}
+knitr::include_graphics("/Users/piza7/Pictures/ResidualPlot.png")
+```
 
@@
 
+```{r, echo=FALSE}
+knitr::include_graphics("/Users/piza7/Pictures/smoothing.png")
+```
+
 (Figure 9): Show identified peaks and valleys
@@
 (Figure 10): Show Aligned Signatures
+
+```{r, echo=FALSE}
+knitr::include_graphics("/Users/piza7/Pictures/AlignedSignatures.png")
+```
 
@@
 
-... to be continued
+## Summary Statistics
+
+[1] implies same comparisons are kept for statistical summary
+
+[2] implies same comparisons are removed for statistical summary
+
+*Span of 15:*
+
+Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+
+0.000   2.000   3.000   3.141   4.000  73.000 [1]
+
+0.000   2.000   3.000   2.872   4.000  34.000 [2]
+
+_____________________________________________________________________________________________
+
+*Span of 25:*
+
+Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+
+0.000   2.000   3.000   3.062   3.000  62.000 [1]
+
+0.000   2.000   2.000   2.827   3.000  37.000 [2]
+
+_____________________________________________________________________________________________
+
+*Span of 35:*
+
+Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+
+0.000   2.000   2.000   2.974   3.000  56.000 [1]
+
+0.000   2.000   2.000   2.776   3.000  32.000 [2]
+
+_____________________________________________________________________________________________
+
+*Span of 45:*
+
+Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+
+0.000   2.000   2.000   2.915   3.000  47.000 [1]
+
+0.000   2.000   2.000   2.745   3.000  37.000 [2]
+
+_____________________________________________________________________________________________
+
+*Span of 55:*
+
+Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+
+0.000   1.000   2.000   2.832   3.000  41.000 [1]
+
+0.000   1.000   2.000   2.685   3.000  34.000 [2]
+
+_____________________________________________________________________________________________
+
+*Span of 65:*
+
+Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+
+0.000   1.000   2.000   2.698   3.000  37.000 [1]
+
+0.000   1.000   2.000   2.569   3.000  34.000 [2]
+
+_____________________________________________________________________________________________
+
+*Span of 75:*
+
+Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+
+0.000   1.000   2.000   2.557   3.000  34.000 [1]
+
+0.000   1.000   2.000   2.442   3.000  25.000 [2]
+
+_____________________________________________________________________________________________
+
+*Span of 85:*
+
+Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+
+0.000   1.000   2.000   2.451   3.000  30.000 [1]
+
+0.000   1.000   2.000   2.349   3.000  23.000 [2]
+
+_____________________________________________________________________________________________
+
+## AUC Calculations No Samp
+
+![Distinct](/Users/piza7/Pictures/Paper_ROC_Distinct.png)
+
+![Non Distinct](/Users/piza7/Pictures/Paper_ROC_NonDistinct.png)
+
+Span of 15: Area under the curve: 0.6414
+
+Span of 25: Area under the curve: 0.6498
+
+Span of 35: Area under the curve: 0.6487
+
+Span of 45: Area under the curve: 0.6577
+
+Span of 55: Area under the curve: 0.6611
+
+Span of 65: Area under the curve: 0.6614
+
+Span of 75: Area under the curve: 0.6606
+
+Span of 85: Area under the curve: 0.6602
+
+```{r eval=FALSE, include=FALSE}
+
+Phoenix_Comparisons_15 <- Phoenix_Comparisons_25 %>%
+  mutate(Bullet1 = gsub(" ", "", fixed = TRUE, Bullet1), Bullet2 = gsub(" ", "", fixed = TRUE, Bullet2))
+
+Phoenix_Comparisons_15 <- Phoenix_Comparisons_15 %>% 
+  mutate(BarrelA = gsub("([A-Z][0-9]|Unknown)-(B[0-9]{1,2}|[0-9A-Z])-([1-6])", "\\1", Bullet2))
+Phoenix_Comparisons_15 <- Phoenix_Comparisons_15 %>% 
+  mutate(BarrelB = gsub("([A-Z][0-9]|Unknown)-(B[0-9]{1,2}|[0-9A-Z])-([1-6])", "\\1", Bullet1))
+Phoenix_Comparisons_15 <- Phoenix_Comparisons_15 %>% 
+  mutate(BulletA = gsub("([A-Z][0-9]|Unknown)-(B[0-9]{1,2}|[0-9A-Z])-([1-6])", "\\2", Bullet2))
+Phoenix_Comparisons_15 <- Phoenix_Comparisons_15 %>% 
+  mutate(BulletB = gsub("([A-Z][0-9]|Unknown)-(B[0-9]{1,2}|[0-9A-Z])-([1-6])", "\\2", Bullet1))
+Phoenix_Comparisons_15 <- Phoenix_Comparisons_15 %>% 
+  mutate(LandA = gsub("([A-Z][0-9]|Unknown)-(B[0-9]{1,2}|[0-9A-Z])-([1-6])", "\\3", Bullet2))
+Phoenix_Comparisons_15 <- Phoenix_Comparisons_15 %>% 
+  mutate(LandB = gsub("([A-Z][0-9]|Unknown)-(B[0-9]{1,2}|[0-9A-Z])-([1-6])", "\\3", Bullet1))
+
+Phoenix_Comparisons_85 <- Phoenix_Comparisons_85 %>% mutate(
+  comparison = paste0(pmin(Bullet1, Bullet2)," vs ", pmax(Bullet1, Bullet2))
+)
+
+```
+
+```{r eval=FALSE, include=FALSE}
+Phoenix_Comparisons_15 <- Phoenix_Comparisons_15 %>% filter(Bullet1 != Bullet2)
+
+Phoenix_Comparisons_15 <- distinct(Phoenix_Comparisons_15, comparison, .keep_all= TRUE)
+
+summary(Phoenix_Comparisons_15$cms)
+
+```
+
+```{r eval=FALSE, include=FALSE}
+Phoenix_Comparisons_25 <- Phoenix_Comparisons_25 %>% filter(Bullet1 != Bullet2)
+
+Phoenix_Comparisons_25 <- distinct(Phoenix_Comparisons_25, comparison, .keep_all= TRUE)
+
+summary(Phoenix_Comparisons_25$cms)
+
+```
+
+```{r eval=FALSE, include=FALSE}
+
+Phoenix_Comparisons_35 <- Phoenix_Comparisons_35 %>% filter(Bullet1 != Bullet2)
+
+Phoenix_Comparisons_35 <- distinct(Phoenix_Comparisons_35, comparison, .keep_all= TRUE)
+
+summary(Phoenix_Comparisons_35$cms)
+
+```
+
+```{r eval=FALSE, include=FALSE}
+
+Phoenix_Comparisons_45 <- Phoenix_Comparisons_45 %>% filter(Bullet1 != Bullet2)
+
+Phoenix_Comparisons_45 <- distinct(Phoenix_Comparisons_45, comparison, .keep_all= TRUE)
+
+summary(Phoenix_Comparisons_45$cms)
+
+```
+
+```{r eval=FALSE, include=FALSE}
+
+Phoenix_Comparisons_55 <- Phoenix_Comparisons_55 %>% filter(Bullet1 != Bullet2)
+
+Phoenix_Comparisons_55 <- distinct(Phoenix_Comparisons_55, comparison, .keep_all= TRUE)
+
+summary(Phoenix_Comparisons_55$cms)
+
+```
+
+```{r eval=FALSE, include=FALSE}
+
+Phoenix_Comparisons_65 <- Phoenix_Comparisons_65 %>% filter(Bullet1 != Bullet2)
+
+Phoenix_Comparisons_65 <- distinct(Phoenix_Comparisons_65, comparison, .keep_all= TRUE)
+
+summary(Phoenix_Comparisons_65$cms)
+
+```
+
+```{r eval=FALSE, include=FALSE}
+
+Phoenix_Comparisons_75 <- Phoenix_Comparisons_75 %>% filter(Bullet1 != Bullet2)
+
+Phoenix_Comparisons_75 <- distinct(Phoenix_Comparisons_75, comparison, .keep_all= TRUE)
+
+summary(Phoenix_Comparisons_75$cms)
+
+```
+
+```{r eval=FALSE, include=FALSE}
+
+Phoenix_Comparisons_85 <- Phoenix_Comparisons_85 %>% filter(Bullet1 != Bullet2)
+
+Phoenix_Comparisons_85 <- distinct(Phoenix_Comparisons_85, comparison, .keep_all= TRUE)
+
+summary(Phoenix_Comparisons_85$cms)
+
+```
 
@@
 
-```{r}
+```{r eval=FALSE, include=FALSE}
 
@@
 
-```{r eval=FALSE}
+```{r eval=FALSE, include=FALSE}
 
@@
    mutate(x3p = map(path, read_x3p))
+
+Phoenix <- Phoenix %>% mutate(x3p = map(x3p, sample_x3p, m = 2, mY = 2))
+
+image(Phoenix$x3p[[1]])
+image(Phoenix$x3p[[11]])
+image(Phoenix$x3p[[111]])
 

### 2020-05-08 Paper.Rmd
Model Summaries Added
Current Progress

@@
 
-![Scan 1 Sampled](/Users/piza7/Pictures/Paper_1_samp.png)
-
 ![Scan 11 Sampled](/Users/piza7/Pictures/Paper_11_samp.png)
@@
 (Figure 2): Regular image of scanned Bullet
-
-![Scan 1](/Users/piza7/Pictures/Paper_1_nosamp.png)
 
@@
 One of these features is CMS, also known as consecutive matching striae.
-We are now able extract the CMS and all the other features associated with bullets land impression.
+We are now able to extract the CMS and all the other features associated with bullets land impression.
 We first smooth the signatures(See Figure 8), identifiy peaks and valleys of each signature(See Figure 9), and align every signature with eachother(See Figure 10).
@@
 
-[1] implies same comparisons are kept for statistical summary
+[1*] implies same comparisons are kept for statistical summary
 
-[2] implies same comparisons are removed for statistical summary
+[2*] implies same comparisons are removed for statistical summary
 
-*Span of 15:*
+```{r}
 
-Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+library(readxl)
+Same_Comparisons_Kept <- read.csv("Book1.csv", header = T)
 
-0.000   2.000   3.000   3.141   4.000  73.000 [1]
+Same_Comparisons_Removed <- read.csv("book2.csv", header = T)
 
-0.000   2.000   3.000   2.872   4.000  34.000 [2]
+```
 
-_____________________________________________________________________________________________
+### Same_Comparisons_Kept
 
-*Span of 25:*
+```{r}
 
-Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+head(Same_Comparisons_Kept, 8)
 
-0.000   2.000   3.000   3.062   3.000  62.000 [1]
+```
 
-0.000   2.000   2.000   2.827   3.000  37.000 [2]
+### Same_Comparisons Removed
 
-_____________________________________________________________________________________________
+```{r}
 
-*Span of 35:*
+head(Same_Comparisons_Removed, 8)
 
-Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+```
 
-0.000   2.000   2.000   2.974   3.000  56.000 [1]
-
-0.000   2.000   2.000   2.776   3.000  32.000 [2]
-
-_____________________________________________________________________________________________
-
-*Span of 45:*
-
-Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
-
-0.000   2.000   2.000   2.915   3.000  47.000 [1]
-
-0.000   2.000   2.000   2.745   3.000  37.000 [2]
-
-_____________________________________________________________________________________________
-
-*Span of 55:*
-
-Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
-
-0.000   1.000   2.000   2.832   3.000  41.000 [1]
-
-0.000   1.000   2.000   2.685   3.000  34.000 [2]
-
-_____________________________________________________________________________________________
-
-*Span of 65:*
-
-Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
-
-0.000   1.000   2.000   2.698   3.000  37.000 [1]
-
-0.000   1.000   2.000   2.569   3.000  34.000 [2]
-
-_____________________________________________________________________________________________
-
-*Span of 75:*
-
-Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
-
-0.000   1.000   2.000   2.557   3.000  34.000 [1]
-
-0.000   1.000   2.000   2.442   3.000  25.000 [2]
-
-_____________________________________________________________________________________________
-
-*Span of 85:*
-
-Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
-
-0.000   1.000   2.000   2.451   3.000  30.000 [1]
-
-0.000   1.000   2.000   2.349   3.000  23.000 [2]
-
-_____________________________________________________________________________________________
+- Looking at the CMS statistics for Same_Comparisons_Removed the lower values of span have higher mean and max statistics.
+The distribution seems to be skewed to the right.
+Now that we have corrected the resolution the CMS statistics are not the same as last time.
+We tended to see the highest average results for spans of 55 to 75.
+These results suggest we perform less smoothing.
 
@@
 Span of 85: Area under the curve: 0.6602
+
+- Notice, for all span values we see slight separability.  The CMS feature does seem to explain some of the models ability to distinquish between Matchs and Non-matches.
+
+## Model Summary RF
+
+*90 10 split*
+
+  Reference
+
+Prediction FALSE TRUE
+
+     FALSE  3729  103
+
+     TRUE     16   72
+
+*80 20 split*
+
+   Reference
+
+Prediction FALSE TRUE
+
+     FALSE  7357  187
+
+     TRUE    133  163
+
+*70 30 split*
+
+   Reference
+
+Prediction FALSE  TRUE
+
+    FALSE 11178   311
+
+    TRUE     57   214
 
@@
 ```
+
+*Span of 15:*
+
+Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+
+0.000   2.000   3.000   3.141   4.000  73.000 [1*]
+
+0.000   2.000   3.000   2.872   4.000  34.000 [2*]
+
+_____________________________________________________________________________________________
+
+*Span of 25:*
+
+Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+
+0.000   2.000   3.000   3.062   3.000  62.000 [1]
+
+0.000   2.000   2.000   2.827   3.000  37.000 [2]
+
+_____________________________________________________________________________________________
+
+*Span of 35:*
+
+Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+
+0.000   2.000   2.000   2.974   3.000  56.000 [1]
+
+0.000   2.000   2.000   2.776   3.000  32.000 [2]
+
+_____________________________________________________________________________________________
+
+*Span of 45:*
+
+Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+
+0.000   2.000   2.000   2.915   3.000  47.000 [1]
+
+0.000   2.000   2.000   2.745   3.000  37.000 [2]
+
+_____________________________________________________________________________________________
+
+*Span of 55:*
+
+Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+
+0.000   1.000   2.000   2.832   3.000  41.000 [1]
+
+0.000   1.000   2.000   2.685   3.000  34.000 [2]
+
+_____________________________________________________________________________________________
+
+*Span of 65:*
+
+Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+
+0.000   1.000   2.000   2.698   3.000  37.000 [1]
+
+0.000   1.000   2.000   2.569   3.000  34.000 [2]
+
+_____________________________________________________________________________________________
+
+*Span of 75:*
+
+Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+
+0.000   1.000   2.000   2.557   3.000  34.000 [1]
+
+0.000   1.000   2.000   2.442   3.000  25.000 [2]
+
+_____________________________________________________________________________________________
+
+*Span of 85:*
+
+Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
+
+0.000   1.000   2.000   2.451   3.000  30.000 [1]
+
+0.000   1.000   2.000   2.349   3.000  23.000 [2]
+
+_____________________________________________________________________________________________

### 2020-05-09 Paper.Rmd
Add files via upload

@@
 
-[1*] implies same comparisons are kept for statistical summary
-
-[2*] implies same comparisons are removed for statistical summary
-
-```{r}
+```{r include=FALSE}
 
 library(readxl)
-Same_Comparisons_Kept <- read.csv("Book1.csv", header = T)
+Same_Comparisons_Removed_Samp <- read_excel("Samp_Book.xlsx")
 
@@
 
-### Same_Comparisons_Kept
-
-```{r}
-
-head(Same_Comparisons_Kept, 8)
-
-```
-
-### Same_Comparisons Removed
+### Same_Comparisons_Removed using dataframe where no sampling was performed
 
@@
 
+### Same_Comparisons Removed using dataframe where sampling was performed
+
+```{r}
+
+head(Same_Comparisons_Removed_Samp, 8)
+
+```
+
+- We first removed Same Land Comparisons from both are nonsampled and sampled dataframes.
+This is to ensure we remove bullet land comparisons we know are already matches.
+We can think of these as outliers and they could have negative effects when it comes to our future random forest model's performance when distinguishing the majority and minority class values.
+
 - Looking at the CMS statistics for Same_Comparisons_Removed the lower values of span have higher mean and max statistics.
-The distribution seems to be skewed to the right.
-Now that we have corrected the resolution the CMS statistics are not the same as last time.
-We tended to see the highest average results for spans of 55 to 75.
+Looking at the CMS statistics for Same_Comparisons_Removed_Samp the lower values of the span have higher mean and max statistics.
+Comparing the CMS values for bullet land scans that did not have sampling performed with bullet land scans that did have sampling performed we see that sampling tends to lower the overall mean cms value.
+Looking at the Max CMS values for bullet land scans where sampling was performed we see higher CMS values at the lower values of span compared to the bullet land scans that did not have sampling performed on them.
 These results suggest we perform less smoothing.
 
-## AUC Calculations No Samp
+Class Seperatability based on CMS span values
 
@@
 
-![Non Distinct](/Users/piza7/Pictures/Paper_ROC_NonDistinct.png)
+## AUC Scores for dataframe where sampling was not performed
 
@@
 
-- Notice, for all span values we see slight separability.  The CMS feature does seem to explain some of the models ability to distinquish between Matchs and Non-matches.
+## AUC Scores for dataframe where sampling was performed
+
+Span of 15: Area under the curve: 0.6496
+
+Span of 25: Area under the curve: 0.6623
+
+Span of 35: Area under the curve: 0.6587
+
+Span of 45: Area under the curve: 0.6519
+
+Span of 55: Area under the curve: 0.6537
+
+Span of 65: Area under the curve: 0.6487
+
+Span of 75: Area under the curve: 0.644
+
+Span of 85: Area under the curve: 0.6378
+
+- Notice, for all span values we see slight separability.
+The CMS feature does seem to explain some of the models ability to distinquish between Matchs and Non-matches.
+All AUC scores were in the mid 60's.
+AUC scores differ between bullet land scans where sampling was not performed and bullet land scans where sampling was peformed.
+For bullets where sampling was not performed we see a span of 55 having the highest AUC value and for bullets where sampling was performed we see a span of 25 having the highest AUC value.
 
@@
 
-*90 10 split*
+Random Forest
 
-  Reference
+#### Span 55 where FALSE is the positive class value
 
-Prediction FALSE TRUE
+#### Same Comparisons kept
 
-     FALSE  3729  103
-
-     TRUE     16   72
-
-*80 20 split*
-
-   Reference
+-----------Reference------------
 
@@
 
-*70 30 split*
+#### Span 55 where FALSE is the positive class value
 
-   Reference
+#### Same comparisons removed
+
+-----------Reference------------
 
@@
 
-    FALSE 11178   311
+    FALSE  3747  104
 
-    TRUE     57   214
+    TRUE      1   48
+
+Accuracy : 0.9731
+
+#### Span 55 sample run where FALSE is the positive class value
+
+#### Same comparisons kept
+
+-----------Reference------------
+
+Prediction FALSE TRUE
+
+    FALSE  7338  205
+
+    TRUE    145  152
+
+#### Span 55 sample run where FALSE is the positive class value
+
+#### Same comparisons removed
+
+-----------Reference-------------
+
+Prediction FALSE TRUE
+
+    FALSE  3738  121
+
+    TRUE      5   36
+
+Accuracy : 0.9677
 

### 2020-05-10 Paper.Rmd
Add files via upload

@@
 With this expanded model, we expect that the algorithm’s results using different CMS calculations will lead to new insights on how 'important' CMS is as a feature and how different CMS impact the Accuracy of two bullets being a match or not a match.
-We perform all of our calculations using the R and mulitple R Programming Language.
-Before we begin to examine the feature known as consecutive matching striae, we will need to perform a number of steps with the bullet scans(edit)
+We perform all of our calculations using the R Programming Language.
+Before we examine the feature known as consecutive matching striae, we will need to perform a number of steps with the bullet scans.
 
 - For this paper we use the Phoenix data set which consist of 198 scanned bullets.
-The scanned bullets are in a .x3p file format of the surface scan between adjacent groove impressions on the bullet and can be read into R using the R package x3ptools.
+The scanned bullets are in a .x3p file format consisting of the surface profile between adjacent groove impressions on the bullet.
+These scans can be read into R using the R package x3ptools.
 For this study we will exam two datasets.
-One Phoenix dataset will have its x3p files containing the scanned bullets down sampled using the x3p_sample() function(See Figure 1).
+One Phoenix dataset will have its x3p files containing the scanned bullets down sampled using the x3p_sample() function(See Figure 2).
 When down sampling is performed the number of pixels in each x3p file are reduced down by a half vertically and horizontally.
-The other Phoenix dataset will have no down sampling performed to the x3p files containg the scanned bullets(See Figure 2).
+The other Phoenix dataset will have no down sampling performed to the x3p files containg the scanned bullets(See Figure 1).
 We examine the scaled measurements of each bullet after being loaded into R.
@@
 
-(Figure 1): Image of scanned Bullet with Reduced Pixels
+(Figure 1): Regular image of scanned Bullet
 
-![Scan 11 Sampled](/Users/piza7/Pictures/Paper_11_samp.png)
+```{r, echo=FALSE}
 
-![Scan 111 Sampled](/Users/piza7/Pictures/Paper_111_samp.png)
+knitr::include_graphics("/Users/piza7/Pictures/Paper_11_samp.png") # Scan 11 No Sample
+knitr::include_graphics("/Users/piza7/Pictures/Paper_111_samp.png") # Scan 111 No Sample
+```
 
-(Figure 2): Regular image of scanned Bullet
+(Figure 2): Image of scanned Bullet with Reduced Pixels
 
-![Scan 11](/Users/piza7/Pictures/Paper_11_nosamp.png)
+```{r, echo=FALSE}
 
-![Scan 111](/Users/piza7/Pictures/Paper_111_nosamp.png)
+knitr::include_graphics("/Users/piza7/Pictures/Paper_11_nosamp.png") # Scan 11 down Sampled
+knitr::include_graphics("/Users/piza7/Pictures/Paper_111_nosamp.png") # Scan 111 down Sampled
+```
 
-- We are now able to analyze the surface scan, by taking a cross section of the surface scan measurements.
+- When comparing bullet scans that were down sampled versus bullet scans that were not down sampled, we see that down sampling removes some tank rash and other markings from the bullet's surface.
+Thus, resulting in smoother images of the scanned bullets.
+
+- We are now able to analyze the surface scan, by taking a cross section of the surface measurements.
 This can be performed using the x3p_crosscut_optimize() function and then next the x3p_crosscut() function.
 Both of which are in the bulletxtrctr R package.
-*Note: We will refer to the surface scan as a land impression from now on.* When plotting the crosscuts we are left with a side profile of the land impressions(See Figure 3).
+*Note: We will refer to the surface scan as a land impression from now on.* When plotting the crosscuts we are left with a side profile of the land impressions.
 Notice the shape of the side profile, it resembles a perfect semi circle.
@@
 These hills are known as shoulders and at the valleys of these shoulders is where the land impression starts and ends.
-The shoulders contain no useful information to date and are removed.
+The shoulders contain no useful information to date and are removed(See Figure 3).
 
-(Figure 3): Side Profile of a bullets land impression
+(Figure 3): Side Profile of land impression before correctly identifying groove cutoffs
+
+```{r, echo=FALSE}
+
+knitr::include_graphics("/Users/piza7/Pictures/Paper_Groove_before_Cut.png")
+
+```
 
 - We begin the process of removing the shoulders.
-First we identify the shoulder locations of each land impression(See Figure 4).
-Second we smooth the land impression(See figure 5).
+First we identify the shoulder locations of each land impression.
+Second we smooth the land impression.
 We then remove the shoulders of the land impression by specifying the left and right shoulder cutoffs.
-Currently this process is trying to be automated using the cc_locate_grooves() function in the bulletxtrctr package but for this study we manually removed the shoulders of the smoothed land impression using a shiny app(See Figure 6).
+Currently this process is trying to be automated using the cc_locate_grooves() function in the bulletxtrctr package but for this study we manually removed the shoulders of the smoothed land impression using a shiny app(See Figure 4).
 
-[[[- Briefly compare the the down-sampled data and the non down-sampled data]]]
-
-(Figure 4): Shoulder locations x2
-
-(Figure 5): Smoothed Impression x2
-
-(Figure 6): Shiny displaying the new groove cutoffs.
-
-![Before Cutoff](/Users/piza7/Pictures/Paper_Groove_before_Cut.png)
-
-![Cutoff](/Users/piza7/Pictures/Paper_Groove_Cut.png)
-
-- After we have identified the groove cutoffs we look for the lowest stable region for each land impression and extract the signatures(See Figure 7).
-The signatures can be obtained using the cc_get_signature() function in the bulletxtrctr package.
-
-(Figure 7): Signature Plot
+(Figure 4): Shiny displaying the new groove cutoffs.
 
 ```{r, echo=FALSE}
-knitr::include_graphics("/Users/piza7/Pictures/ResidualPlot.png")
+
+knitr::include_graphics("/Users/piza7/Pictures/Paper_Groove_Cut.png")
+
 ```
+
+- After we have identified the groove cutoffs we look for the lowest stable region for each land impression and extract the signatures.
+The signatures can be obtained using the cc_get_signature() function in the bulletxtrctr package.
 
@@
 One of these features is CMS, also known as consecutive matching striae.
-We are now able to extract the CMS and all the other features associated with bullets land impression.
-We first smooth the signatures(See Figure 8), identifiy peaks and valleys of each signature(See Figure 9), and align every signature with eachother(See Figure 10).
+We are now able to extract the CMS and all the other features associated with a bullets land impression.
+We first smooth the signatures(See Figure 8 & 9), identifiy peaks and valleys of each signature(See Figure 10), and align every signature with eachother(See Figure 11).
 When the two signatures are aligned we are able to identify the matching peaks and valleys which coincide to the striation marks left on a bullet's surface after being fired(See figure 11).
@@
 ```{r, echo=FALSE}
+knitr::include_graphics("/Users/piza7/Pictures/Rplot_A9-B1-1_reg.png")
+knitr::include_graphics("/Users/piza7/Pictures/Rplot_A9-B1-1_Smoothed.png")
+```
+
+(Figure 9): Smoothing Overlayed
+
+```{r, echo=FALSE}
 knitr::include_graphics("/Users/piza7/Pictures/smoothing.png")
@@
 
-(Figure 9): Show identified peaks and valleys
-
-(Figure 10): Show Aligned Signatures
+(Figure 10): Show identified peaks and valleys
 
 ```{r, echo=FALSE}
-knitr::include_graphics("/Users/piza7/Pictures/AlignedSignatures.png")
+knitr::include_graphics("/Users/piza7/Pictures/Rplot_A9-B1-1_Idnt_P&V.png")
+```
+
+(Figure 11): Show Aligned Signatures
+
+```{r, echo=FALSE}
+
+knitr::include_graphics("/Users/piza7/Pictures/Rplot_A9-B1-1vsA9-B2-6_Jitter.png")
+
 ```
@@
 
+#Same_Comparisons_Removed <- Same_Comparisons_Removed %>% select(-X)
+
 head(Same_Comparisons_Removed, 8)
@@
 
-- We first removed Same Land Comparisons from both are nonsampled and sampled dataframes.
+- We first removed Same Land Comparisons from both the nonsampled and sampled dataframes.
 This is to ensure we remove bullet land comparisons we know are already matches.
-We can think of these as outliers and they could have negative effects when it comes to our future random forest model's performance when distinguishing the majority and minority class values.
+We can think of these as sorta outliers and they could have negative effects when it comes to our future random forest model's performance when distinguishing the majority and minority class values.
 
@@
 Looking at the CMS statistics for Same_Comparisons_Removed_Samp the lower values of the span have higher mean and max statistics.
-Comparing the CMS values for bullet land scans that did not have sampling performed with bullet land scans that did have sampling performed we see that sampling tends to lower the overall mean cms value.
+Comparing the CMS values for bullet land scans that did not have sampling performed with bullet land scans that did have sampling performed; we see that sampling tends to lower the overall mean cms value.
 Looking at the Max CMS values for bullet land scans where sampling was performed we see higher CMS values at the lower values of span compared to the bullet land scans that did not have sampling performed on them.
-These results suggest we perform less smoothing.
+This could make our previous statement less justifiable.
+These results suggest we perform less smoothing or at least avoid very high span values when we smooth.
 
@@
 
-- Notice, for all span values we see slight separability.
+- Notice, for all the span values we see slight separability.
 The CMS feature does seem to explain some of the models ability to distinquish between Matchs and Non-matches.
@@
 AUC scores differ between bullet land scans where sampling was not performed and bullet land scans where sampling was peformed.
-For bullets where sampling was not performed we see a span of 55 having the highest AUC value and for bullets where sampling was performed we see a span of 25 having the highest AUC value.
+For bullets where sampling was not performed we see a span of 65 having the highest AUC value and for bullets where sampling was performed we see a span of 25 having the highest AUC value.
+
+## Random Forest Model
+
+- Data where span = 55 was used to train and test our random forest model.
+We train a model using the down sampled bullet scans and we train another model using the data where the bullet scans were not sampled.
+We also train each using the full dataset where the same bullet comparisons are kept and where the same bullet comparisons are removed.
+So we have a total of 2 x 2 = 4 models.
+Feature selection and cross validation were used for training and testing the random forest models.
+This was done using a custom cross validation loop that applies feature selection to the training data within each fold.
+Previous studies, important variables determined by random forest, and boruta feature selection suggested using columns: ccf, rough_cor, D sd_D, matches, mismatches, cms, non_cms, and sum_peaks out of the (20~25) original columns.
+Looking at the results, we notice that using data where the same land comparisons were kept lowers the random forest models overall performance.
+We see slightly better performance when we remove the same comparisons, leaving only distinct values.
+The results also show that down sampled bullet scans hurt our random forest models over all performance.
+We only tried down sampling using x3p_sample(m = 2, mY = 2), there might be better results using different parameter values for x3p_sample()...
+to be continued.
+We show the output of the confusion matrix and calculate precision, recall, F-measure, and Class Balance Accuracy to get a better understanding of our models performance.
+The models ability to distinguish between matches and non-matches is quite low.
+This is most likely due to class imbalance from our target variable.
 
@@
 
-#### Span 55 where FALSE is the positive class value
+### Span 55 where FALSE is the positive class value
 
 #### Same Comparisons kept
+
+    Precision = 7357/(7357+187) = .9752
+
+    Recall = 7357/(7357+133) = 0.9822
+
+    F-measure(Harmonic Mean) = 2(7357)/(2(7357)+187+133) = 0.9787
+
+    CBA_p = 7357/max{7357+187, 7357+133} = .9752
+
+    CBA_n = 163/max{163+187, 163+133} = 0.4657
+
+    CBA = (CBA_p + CBA_n)/2 = 0.7204
 
@@
 
-#### Span 55 where FALSE is the positive class value
+### Span 55 where FALSE is the positive class value
 
 #### Same comparisons removed
+
+    Precision = 3747/(3747+104) = 0.9729
+
+    Recall = 3747/(3747+1) = 0.9997
+
+    F-measure(Harmonic Mean) = 2(3747)/(2(3747)+104+1) = 0.9861
+
+    CBA_p = 3747/max{3747+104, 3747+1} = 0.9729
+
+    CBA_n = 48/max{48+104, 48+1} = 0.3157
+
+    CBA = (CBA_p + CBA_n)/2 = 0.6443
 
@@
 
+    Precision = 7338/(7338+205) = 0.9728
+
+    Recall = 7338/(7338+145) = 0.9806
+
+    F-measure(Harmonic Mean) = 2(7338)/(2(7338)+205+145) = 0.9767
+
+    CBA_p = 7338/max{7338+205, 7338+145} = 0.9728
+
+    CBA_n = 152/max{152+205, 152+145} = 0.4257
+
+    CBA = (CBA_p + CBA_n)/2 = 0.6992
+
 -----------Reference------------
@@
 
+    Precision = 3738/(3738+121) = 0.9686
+
+    Recall = 3738/(3738+5) = 0.9986
+
+    F-measure(Harmonic Mean) = 2(3738)/(2(3738)+121+5) = 0.9834
+
+    *CBA_p = 3738/max{3738+121, 3738+5} = 0.9686*
+
+    *CBA_n = 36/maax{36+121, 36+5} = 0.2292*
+
+    CBA = (CBA_p + CBA_n)/2 = 0.5989
+
 -----------Reference-------------
@@
 Accuracy : 0.9677
+
+## Conclusion
 

### 2020-05-11 Paper.Rmd
Add files via upload

@@
 ## Conclusion
+
+- We explored the CMS feature and sought ways to improve it.
+The span value does play an impact on the number of consecutive matching striation marks.
+Span values and sampling also play a role  when it comes to machine learning model performance but do not seem to increase the overall value of consecutive matching striae.
+This leads us to believe the current way CMS is calculated may need to be adjusted.
+When exploring two aligned signatures there was strong evidence for higher CMS values than what was actually calculated.
+This was found by individually looking at aligned signature plot and observing the matching peaks and values.
+Currently the CMS values outputed seems to be too low for some bullet comparisons.
 
